


\section{From Anouck} 

\begin{itemize} Root Finding: Applications to find equilibria of nonlinear systems, to find conditions for linearization.

 

Scaling up to large sets of equations (thousands of variables) through vectors, matrices, determinants, and matrix inverses.

 

Vectors, matrices form the basis of state space control theory (ROB535, but also graduate level Linear Systems (different numbers in different departments), Linear Feedback Control)

 

·  Regression as a means of building models and making predictions.

 

ROB535, AEROSP740 Model Predictive Control. Both courses teach MPC (AEROSP740 in more details). MPC combines prediction and optimization to try to correct errors before they happen.

 

·  A camera pin-hole model and camera calibration via regression.

 

Basics of computer vision are covered in ROB535

 

·  Concept of factoring a matrix. Inner products and orthogonal vectors. Symmetric matrices and orthogonal matrices.

 

Certainly useful in linear systems and linear feedback.

 

·  Finding solutions to nonlinear equations via gradient descent.

·  Optimization as a tool for solving robot perception problems.

 

Optimization and nonlinear equations covered in ROB535 in the context of trajectory optimization for self-driving cars.

 

·  Linear transformations with applications to spatial coordinates.

·  LiDAR point clouds and blobs.

 

Covered also in ROB535

 

·  Accelerometers, single-axis gyroscopes, encoders, and what is an ODE.

 

Covered some in 535, and also covered in AEROSP584 Navigation and Guidance.

 

